Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2015-01-20 draft_lm1.tex
added a subsection describing the data. Closes issue #4.

In this section we will start by describing a method to estimate the 
effective 
reproductive number, $R_t$, and obtain its 
posterior distribution. 
We then proceed to describe Susceptible-infectious-recovered (SIR) model 
used to represent the global disease incidence and how $R_t$ can be integrated 
into the model to allow for time varying transmission. 
Next, an approach to approximate the posterior distributions 
of the numbers of susceptible to the main circulating Dengue viruses for each 
epidemic is detailed.
Finally, we discuss how to estimate the attack ratio of each 
epidemic using the estimated susceptible fraction and observed incidence.
We employ these methods to analyze Dengue weekly incidence time series for the 
city of Rio de Janeiro from 1996 to 2014.

>>>>

In this section we will start by describing the data and then the method used 
to estimate the effective reproductive number, $R_t$, from the data and obtain 
its posterior distribution. 
We then proceed to describe Susceptible-infectious-recovered (SIR) model 
used to represent the global disease incidence and how $R_t$ can be integrated 
into the model to allow for time varying transmission. 
Next, an approach to approximate the posterior distributions 
of the numbers of susceptible to the main circulating Dengue viruses for each 
epidemic is detailed.
Finally, we discuss how to estimate the attack ratio of each 
epidemic using the estimated susceptible fraction and observed incidence.

\subsection{The dataset} 
The data used in this paper consists of  Dengue weekly notified cases time 
series for the city of Rio de Janeiro from 1996 to 2014. The cases are notified 
based only on clinical symptoms. Laboratory confirmation and serotype 
information are available only for a very small sample and only on recent 
years (2010-2013).
